\documentclass[a4paper, 12pt]{article}

\usepackage[scale=0.75]{geometry}

\usepackage{fontspec}
\setmainfont[Ligatures=TeX]{Linux Libertine}

\usepackage[british]{babel}
\usepackage{multirow}
\usepackage{mdwlist}
\usepackage{footnote}
\usepackage{float}

\makesavenoteenv{tabular}

\title{Old/New 2012}
\author{The DF Movement}
\date{12th-14th October 2012}

\setcounter{tocdepth}{2}

\begin{document}
\maketitle
\tableofcontents

\clearpage

\section{Committee, Council and Non-Committee Roles}
%See Tables \ref{tab:ctte} and \ref{tab:council} for details of roles and people occupying them.
\begin{savenotes}
\begin{table}[H]
\centering

\begin{tabular}{ l || l | l }
\textbf{Role}				& \textbf{Old}			& \textbf{New} \\ \hline
Affiliations				& Laurie Canell			& Ellie Ferguson \\
Campaigns					& Will Searby			& Rosie Booth \\
Communications				& Louise Delmége		& Louise Delmége (re-elected) \\
Events						& Michael Sargent		& Ruori McIntyre \\
Fundraising					& Samir Rana			& Joe F. Bowler (Jay) \\
International				& Imogen Smith			& Imogen Smith (continuing) \\
Projects					& Emily Connor			& Emily Connor (continuing) \\
Training					& Anna Robson			& Saskia Neibig \\
Treasurer					& Saul Russell-Moyle	& [unfilled]\footnote{RON was elected at Althing, and financial responsibility has fallen to General Council as per section B.1.7.2 of the Constitution.} \\
Secretary					& James Robson			& Joe MacMahon (Kess) \\
Shadow Treasurer			& [unfilled]			& Ellie Mestel \\
Chair of Regional Council	& KT Moon				& Emma Jagne \\
Lay Member 1				& Sian Leary			& [unfilled] \\
Lay Member 2				& Jess Poyner			& Jess Poyner (continuing) \\
Chair						& Louise Delmége		& Jess Poyner \\
Vice-Chair					& Jess Poyner			& Saskia Neibig \\
General Council Rep			& ?						& Louise Delmége \\
Sustainability				& Sian Leary			& Emily Connor \\
Staff Liaison				& ?						& Saskia Neibig \\
\end{tabular}
\caption{DF Committee}
\label{tab:ctte}
\end{table}
\end{savenotes}

\begin{savenotes}
\begin{table}[H]
\centering

\begin{tabular}{ l || l | l }
\textbf{Role}		& \textbf{Old}		& \textbf{New} \\ \hline
Scotland			& Adi Childs		& Adi Childs (continuing) \\
North West			& Annie Tothill		& Ellie Willams \\
North East			& Sam Townsend		& Adam Fidler\footnote{Standing down after NE Thing.} \\
Wales				& Emma Jagne		& Leonor Worssam \\
Midlands			& Lily Bowler		& Alice Hall and Meg Beamish\footnote{Elected jointly to the role.} \\
East				& Ellie Ferguson	& [unfilled] \\
SWAN				& \multirow{2}{*}{Sarah Barker\footnote{South West Rep was split this year into SWAN and OSG -- South West Area Network and Oxford-Swindon-Gloucester.}} & \multirow{2}{*}{Samir Rana\footnote{Elected to both SWAN and OSG}} \\
OSG					& 					&  \\
South East			& Esme Sarfas		& Ruth O'Sullivan \\
London				& Kieran Kirkwood	& [unfilled] \\
Chair				& KT Moon			& Emma Jagne \\
General Council Rep	& ?					& Leonor Worssam \\
\end{tabular}
\caption{Regional Council}
\label{tab:council}
\end{table}
\end{savenotes}

\begin{savenotes}
\begin{table}[H]
\centering

\begin{tabular}{ l || l | l }
\textbf{Role}			& \textbf{Old}			& \textbf{New} \\ \hline
Webfairy				& Joe MacMahon			& [unfilled] \\
Zine Editor				& Sophie Slater			& Jack Lynch \\
First-Aid Rep			& [role non-existant]	& Mez Griffin \\
MEST-UP Co-ordinator	& [role non-existant]	& KT Moon \\
\end{tabular}
\caption{Non-Committee Roles}
\label{tab:nonctte}
\end{table}
\end{savenotes}

\subsection{Attendance}
In attendance: Verity Jones (observing), Saskia Neibig, Anna Robson, Meg Beamish, Lily Bowler, Joe F. Bowler (Jay), Joe MacMahon (Kess), Louise Delmége, Jess Poyner, Emma Jagne, KT Moon, Ruori McIntyre, Ruth O'Sullivan, Samir Rana, Laurie Canell, Annie Tothill, Alice Hall, Emily Connor, Leonor Worssam, Rosie Booth, Ellie Ferguson, Ellie Williams, Saul Russel-Moyle, Jack Lynch, Ellie Mestel.

Apologies from: Michael Sargent

\section{Brainstorming Session for Next Year}
Open-space discussion used to share ideas for 6 questions.
\subsection{What worked well in DFs this year?}
\begin{itemize*}
	\item Lots of new DFs
	\item Almost every procedure we have was used at Althing
	\item The Share and Lammas training
	\item Website
	\item Ceilidh band vaguely formed
	\item Workshops at Spring Awakening (particularly Seeds of Change)
	\item Publicity of events and stuff on Facebook and SpanThatWorld
	\item Wunderbar at DF Camp (particularly Chai Amaretto)
	\item Valentines hostel
	\item We didn't get kicked out of Winter Wonderland (South) venue
	\item Gained trust from Height Gate
	\item MEST-UP at events, and lots of people MEST-UP trained
\end{itemize*}

\subsection{What do we want to achieve next year?}
\begin{itemize*}
	\item Ace V-CAMP!
	\item Bigger events
	\item Better attended events
	\item Better advertised (through RC?)
	\item More Roots Fund stuff (events?) (particularly to link with young leaders, and involve training)
	\item More spending
	\item Zines
	\item Build relationships with other organisations
	\item Help Woodcraft break even for the first time (as part of the 5-year financial plan)
	\item Earn more money and spend it on stuff
	\item First-aid training
	\item Have a successful Winter Wonderland (don't get banned from the venue)
	\item More project-related workshops (working groups)
	\item The Share
	\item Make events more accessible to skint people
	\item Use Hamsterly before it shuts
	\item Produce and awesome and capable generation of DFs
	\item Less Althing motions
\end{itemize*}

\subsection{How will we know when we've achieved it?}
\begin{itemize*}
	\item More money goes out of the fund on cool stuff!
	\item New DFs
	\item Know where you are when beginning -- collect `baseline' info; have clear targets
	\item More applications for roots fund
	\item Good feedback from Venturer Camp
	\item Bigger events, better attended
	\item More DFs coming to events
	\item New districts participating in national things!
	\item Lots of happy DFs (viz. Happy Laurie and Happy Annie)
	\item More DFs going to training weekends + international events
\end{itemize*}

\subsection{How will we share what we've done with non-Ctte DFs/the movement at large?}
\begin{itemize*}
	\item Make resources
	\item Courier
	\item Zines
	\item At district level (Regional reps?) -- go to district meetings and regional AGMs
	\item Send email: ``This week on SpanThatWorld...''
	\item VIDEOS
	\item SpanThatWorld
	\item At events, VCamp
	\item Emails
	\item Woodcraft website
	\item Regional online newsletters?
	\item Facebook
	\item TREE mailings
	\item Publish minutes quickly\footnote{Sorry... these minutes brought to you by Mon. 17th Dec 2012.}
	\item `What has Ctte been up to?' videos/blogs
\end{itemize*}

\subsection{Where can we go for support?}
\begin{itemize*}
	\item Head office
	\item General Council (chair@woodcraft.org.uk)
	\item Trade unions
	\item Training events
	\item Jack Brown
	\item Vice chair + Chair of Ctte
	\item District leaders
	\item Lay members
	\item Other DFs
	\item Rich people
	\item Like-minded organisations
	\item Mentors! (Previous Ctte/RC members?)
	\item BYC
	\item Other youth organisations (Scouts?)
\end{itemize*}

\subsection{How are we going to achieve our goals?}
\begin{itemize*}
	\item Events organised way in advance
	\item Organisation
	\item Facebook
	\item Emails
	\item Videos
	\item Link up with GC and subcommittees
	\item Good communication between Ctte, Council and other DFs
	\item Train ourselves
	\item Get the rest of the movement involved! Delegate, delegate, delegate...
	\item EVERYONE USE CRABGRASS!
\end{itemize*}

\section{Motions}
Eight motions were carried over to Old/New from Althing as there wasn't time to discuss them.
\subsection{Motion 29: Food hygiene (passed)}
This DF althing recognises the importance of food hygiene at DF events and that while all foods should be stored and prepared in a safe and clean environment, some foods require different or more demanding care.

This DF Althing therefore resolves to:
\begin{itemize*}
	\item Action the Events rep to add a section on food hygiene in the Events pack.
	\item Advise KPs to never use ingredients they are: not comfortable with, inexperienced with or do not have the facilities to store properly.
	\item Reaffirm the KP's responsibility to keeping all food preparation and storage areas clean and functional.
\end{itemize*}

No rationale given.

Proposed by Issy Coleman.

Motion passes 16-0 (4 abstentions).

\subsection{Motion 33: Legal drugs () (passed as amended)}
This Althing would like to recognise that legal drugs can be just as harmful to one's health, sometimes more so, than illegal drugs. Therefore the DF Movement discourages the use of any drug if the user is not absolutely happy in their knowledge of:
\begin{enumerate*}
	\item Its contents
	\item What effects it can have
	\item The quantities in which it is safe to consume.
\end{enumerate*}

Rationale: Legal highs can be worse health-wise if you end up in hospital. Staff see lots of overdoses in most illegal drugs, and thus know what chemicals are involved and the best treatments.

Proposed by Ellie Ferguson.

\subsubsection{Amendment (accepted)}
Summary to be included in Drugs and Alcohol policy to be read out at events.

Proposed by Joe MacMahon (Kess).

Amendment accepted by proposer.

Motion as amended passes unopposed.

\subsection{Motion 35: Membership fees (passed)}
This DF Althing instructs the Events Rep, Secretary and Chair to ensure that every person attending a DF event has paid membership fees and every one that needs it has an up to date CRB.

In order to do this we suggest they:
\begin{enumerate*}
	\item The week before an event they send all the names of those booked to someone with access to the membership database and ask them to check those people.
	\item Tell anybody that isn't a member that they will be turned away if they don't pay for and fill in a form for membership on camp. On the event, chase up those that book in the last week.
\end{enumerate*}

No rationale given.

Proposed by Laurie Canell.

\subsubsection{Amendment (withdrawn)}
Look into creating a policy about lying on booking forms.

Proposed by Saskia Neibig.

Amendment rejected by proposer and withdrawn.

Motion passes 18-0 (3 abstentions)

\subsection{Motion 38: Gift Aid (passed as amended)}
This Althing [demands] that the Events Rep and Treasurer provide the option to gift aid donations of event costs. [*]

No rationale given.

Proposed by Joe F. Bowler (Jay).

\subsubsection{Amendment 1 (accepted)}
Replace ``demands'' with ``strongly recommends''.

Proposed by Joe MacMahon (Kess).

Accepted by proposer.

\subsubsection{Amendment 2 (accepted)}
Append ``And explain to people how gift aid works.''

Proposed by Jess Poyner.

Accepted by proposer.

Motion passes unopposed.

\subsection{Motion 39: Committee quarterly reports (passed as amended)}
This Althing reaffirms the demand that all members of Committee provide 1/4ly update reports even if they do not attend Things. This is already in the Constitution. [*]

No rationale given.

Proposed by Joe F. Bowler (Jay).

\subsubsection{Amendment (accepted)}
Append ``*raised eyebrows*''.

Proposed by Ruori McIntyre.

Accepted by proposer.

Motion passes unopposed.

\subsection{Motion 42: Event Mentors (passed as amended)}
This DF Althing instructs that when DFs are part of a coordination team for the first time they should have a `Mentor' that they can contact for advice and help before and at the event.

The mentors would either be experienced DFs or Kinsfolk -- preferably someone attending the event but at least contactable by phone.

Rationale: This would help organisation, cooperation of coordination team, menu planning and the general smooth running of future events.

Proposed by Issy Coleman.

\subsubsection{Amendment (passed)}
Potential mentees should be given the option to have a mentor or not.

Proposed by Louise Delmége.

Amendment passes unopposed.

Motion passes unopposed.

Note from Verity: Would be good to have mentors trained centrally by Woodcraft -- there is a mentoring training weekend next weekend. Also there are mentors available from central Woodcraft already.

\subsection{Motion 44 (withdrawn)}
Not to be discussed as previous motion passed.

\subsection{Motion 53 (amended, tabled)}
This Althing instructs the Treasurer to seek to fund Woodcraft's mission through our investments. We aim to fund companies with similar values of peace, co-operation and education for social change.

We aim to withdraw investment from companies profiting from the arms trade, exploitation, human rights abuse and climate change.

[*] This Althing instructs the Treasurer to take reasonable steps to move DF funds to an ethical bank such as Triodos. If this is not practical for all of the funds, it should be attempted for an appropriate amount, such as the majority.

Proposed by (we think) Sam Sender.

\subsubsection{Amendment (passed)}
Prepend final paragraph with ``Therefore''. Capitalise accordingly.

Proposed by Emma Jagne.

Amendment passes unopposed.

\subsubsection{Proposal}
Tablue until next Althing because of current Treasurer issues.

Proposed by Samir Rana.

Proposal passes 15-1 (2 abstentions)

Motion tabled.

\subsection{Remaining motions}
At Althing, some un-discussed motions were also sent to ``a social event'', and ``a Thing'', to be decided by Old/New.

Social event: Winter Wonderland (unanimous).

Thing: North East Thing (unopposed).

\section{Internal Elections}
Note: The positions elected in internal elections are also shown in Tables \ref{tab:ctte} and \ref{tab:council}
\subsection{Regional Council}
Emma Jagne elected as Chair.

Samir Rana elected as Vice Chair.

Leonor Worssam elected as General Council Rep.

\subsection{DF Committee}
Saskia Neibig elected as Staff Liaison.

Emily Connor elected as Sustainability

Louise Delmége elected as General Council Rep.

Saskia Neibig elected as Vice Chair.

Jess Poyner elected as Last Bastion of Hope (Chair).

\section{Treasurer/Finance discussion}
It was discussed what to do about the lack-of-Treasurer situation. Committee have the option of co-opting somebody to the role of Treasurer with a 2/3rds majority, or otherwise management of finances falls to General Secretary, Chair and Treasurer of central Woodcraft.

One candidate was nominated for co-opting, but we decided to let responsibility fall to central Woodcraft.

\subsection{Logistics}
At this point, it was assumed that the General Secretary, Chair of GC and Treasurer would find somebody and delegate to them the task of managing our finances. We require the following of them:
\begin{itemize*}
	\item That they aim to carry through financial decisions made at Althing.
	\item That they make payments within 3 months.
	\item To maintain a minimum of £20,000 in the DF bank account.
	\item To have DF Committee approve budgets, asking for the input of the central Woodcraft Treasurer.
	\item That they make arrangements for the training of the Shadow Treasurer, be that training them themselves or finding somebody else to train them.
	\item That they attend DF Things or send apologies.
\end{itemize*}

As soon as Ellie M is a signatory, she should organise Fairer Fare and expenses as this isn't too difficult. Saul should do Althing and Old/New expenses for the time being.

The process of finding a Treasurer should be completed sufficiently quickly to avoid any potential financial problems with paying for Winter Wonderland.

Richard Lace was suggested as a potential candidate to recommend.

The following people should be signatories on the bank account: Treasurer, Shadow Treasurer, Chair, Secretary, Events, Fundraiser.

Saul has written up four alternatives for next year's budget, these are to be passed on to the new Treasurer.

\section{Table of Actions}


\end{document}